---
title: "Initial EDA - 136 farms"
author: "A T Chamberlain"
date: "2024-07-24"
output: word_document
---

# NOTES
# 24 July - increased from 105 to 136 herds - these are all routine HPRs from Emma 
# 25 July - start sensible outlier checking - have removed 6+9 for BF + culling = 5% 
# 13 Aug - 149 files, better data processing - hopefully finalversion of data

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# set up libraries required installing them first if need be. - do I need all of these 
if(!require("tidyverse")) install.packages("tidyverse")
if(!require("plotly")) install.packages("plotly")
if(!require("lubridate")) install.packages("lubridate") # date handling 
if(!require("Hmisc")) install.packages("Hmisc")
if(!require("hms")) install.packages("hms") 
if(!require("robustbase")) install.packages("robustbase") 
if(!require("matrixStats")) install.packages("matrixStats") 
if(!require("openxlsx")) install.packages("openxlsx") 
if(!require("broom")) install.packages("broom") 
if(!require("PerformanceAnalytics")) install.packages("PerformanceAnalytics") 
if(!require("Hmisc")) install.packages("Hmisc")

# clear out any current variables etc
rm(list = ls())

```

```{r load data, echo=FALSE}

setwd("C:/ATC_data/HPRs/Paper_Eric_OEE+LCA")
getwd()

data = read_csv("C:/ATC_data/HPRs/Paper_Eric_OEE+LCA/Data_149herds_13Aug24.csv")

farmNumber = 1

if (farmNumber == 1) {farmName = "HAU_main"}
if (farmNumber == 2) {farmName = "HAU_AMS"}
if (farmNumber == 3) {farmName = "MaGo"}
if (farmNumber == 4) {farmName = "PrSt CBA"}
if (farmNumber == 5) {farmName = "StWe MVF"}

  
print("Herd number")
print(farmNumber)
print("Herd Name")
print(farmName)
print("Herd ID")
print(data$farmID[farmNumber])

# sort out some missing data in case they exist 
# check class and only doing those where class = chr 

missingStrings = c("N/A", "NA", "na", "#N/A", "nan", "#VALUE!", "#NAME?" )

if (is.character(data$Cull_L6) == "TRUE") {
  temp = as.character(data$Cull_L6)
  temp = parse_number(temp,na = missingStrings)
  data$Cull_L6 = as.double(temp) 
}

if (is.character(data$Cull_L6over) == "TRUE") {
  temp = as.character(data$Cull_L6over)
  temp = parse_number(temp,na = missingStrings)
  data$Cull_L6over = as.double(temp) 
}


```



```{r 1st EDA, echo=FALSE}
 # some initial EDA 
# fill = "darkseagreen", colour = "darkslategrey"

# pull out data point for a specific herd - here is is herd 1 which is HAU
xpoint = data$annualMY[farmNumber]
ypoint = 7

# create the percentile distribution
percentile = ecdf(data$annualMY)
# where does farm 1 lie on this distribution
m = 100* percentile(xpoint)
 # is.integer(m)
m = round(m+0.5,0)
m = as.integer(m)
 # is.integer(m)
m = as.character(m)
# using paste() to concatenate two strings
result = paste("Percent of herds in dataset that have a value lower than this farm = ", m)

p = ggplot(data, aes(x=annualMY))+
  geom_histogram(binwidth =250,fill = "cadetblue1", colour = "deepskyblue4" )+
      labs(y = "herds", 
        x = "Annual milk yield (kg/cow/year)", 
        title = "EDA - spread of milk yields",
        subtitle = "136 herds - as at 24July24",
        caption = result ) + 
         geom_point(aes(x=xpoint,y=ypoint), color="blue", size = 5)  +
     geom_label(
    label=farmName, 
    x=xpoint*1.03,
    y=ypoint*1.2,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.35,
    color = "bisque4",
    fill="bisque")

plot(p)

print ("Value for this herd :")
print(data$annualMY[farmNumber])

summary(data$annualMY)

min(data$annualMY)
max(data$annualMY)

minHerd = which.min(data$annualMY)
maxHerd = which.max(data$annualMY)

data$farmID[minHerd] 
data$farmID[maxHerd] 

# pull out data point for a specific herd - here is is herd 1 which is HAU
xpoint = data$herdSize[farmNumber]
ypoint = 10

# create the percentile distribution
percentile = ecdf(data$herdSize)
# where does farm 1 lie on this distribution
m = 100* percentile(xpoint)
 # is.integer(m)
m = round(m+0.5,0)
m = as.integer(m)
 # is.integer(m)
m = as.character(m)
# using paste() to concatenate two strings
result = paste("Percent of herds in dataset that have a value lower than this farm = ", m)

p = ggplot(data, aes(x=herdSize))+
  geom_histogram(binwidth =50 ,fill = "cadetblue1", colour = "deepskyblue4" )+
      labs(y = "herds", 
        x = "Cows in herd", 
        title = "EDA - herd size",
        subtitle = "136 herds - as at 24July24",
        caption = result) +
          geom_point(aes(x=xpoint,y=ypoint), color="blue", size = 5)  +
     geom_label(
    label=farmName, 
    x=xpoint*1.13,
    y=ypoint*1.35,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.35,
    color = "bisque4",
    fill="bisque")

plot(p)

print ("Value for this herd :")
print(data$herdSize[farmNumber])

summary(data$herdSize)

# find the highest and lowest values 
# sort into a temp dataframe
tempData = data[order(data$herdSize),]
# look at top and bottom 
# head(tempData,10)
# tail(tempData)

```

```{r 1st EDA - milk composition, echo=FALSE}

# Look to see if any should be excluded as probably not Fr/Hol

# pull out data point for a specific herd - here is is herd 1 which is HAU
xpoint = data$BFAnnualAvg[farmNumber]
ypoint = 7
# create the percentile distribution
percentile = ecdf(data$BFAnnualAvg)
# where does farm 1 lie on this distribution
m = 100* percentile(xpoint)
 # is.integer(m)
m = round(m+0.5,0)
m = as.integer(m)
 # is.integer(m)
m = as.character(m)
# using paste() to concatenate two strings
result = paste("Percent of herds in dataset that have a value lower than this farm = ", m)


p = ggplot(data, aes(x=BFAnnualAvg))+
  geom_histogram(binwidth =.1 ,fill = "cadetblue1", colour = "deepskyblue4" )+
      labs(y = "herds", 
        x = "Annual average BF(%)", 
        title = "EDA - Butter fat",
        subtitle = "136 herds - as at 24July24",
        caption = result)+
           geom_point(aes(x=xpoint,y=ypoint), color="blue", size = 5)  +
     geom_label(
    label=farmName, 
    x=xpoint*1.13,
    y=ypoint*1.35,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.35,
    color = "bisque4",
    fill="bisque")

plot(p)

print ("Value for this herd :")
print(data$BFAnnualAvg[farmNumber])

summary(data$BFAnnualAvg)

# find the highest and lowest values 
# sort into a temp dataframe
tempData = data[order(data$BFAnnualAvg),]
# head(tempData,10)
# tail(tempData,10)

# ACTION - exclude all herds where BF > 5% 

data = data[data$BFAnnualAvg < 5.0 , ]

# pull out data point for a specific herd - here is is herd 1 which is HAU
xpoint = data$FPcorrfactor[farmNumber]
ypoint = 7
# create the percentile distribution
percentile = ecdf(data$FPcorrfactor)
# where does farm 1 lie on this distribution
m = 100* percentile(xpoint)
 # is.integer(m)
m = round(m+0.5,0)
m = as.integer(m)
 # is.integer(m)
m = as.character(m)
# using paste() to concatenate two strings
result = paste("Percent of herds in dataset that have a value lower than this farm = ", m)

p = ggplot(data, aes(x=FPcorrfactor))+
  geom_histogram(binwidth =.025 ,fill = "cadetblue1", colour = "deepskyblue4" )+
      labs(y = "herds", 
        x = " FP Corr factor", 
        title = "EDA - FP Corr factor",
        subtitle = "136 herds - as at 24July24",
        caption = result)+
           geom_point(aes(x=xpoint,y=ypoint), color="blue", size = 5)  +
     geom_label(
    label=farmName, 
    x=xpoint*1.1,
    y=ypoint*1.35,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.35,
    color = "bisque4",
    fill="bisque")
plot(p)

print ("Value for this herd :")
print(data$FPcorrfactor[farmNumber])

summary(data$FPcorrfactor)

# are Corr value and BF related? 

ggplot(data, aes(x=BFAnnualAvg, y=FPcorrfactor))+
  geom_point(size = 2)

cor(data$BFAnnualAvg,data$FPcorrfactor)

# they are very related - reject herds with BF over 5% as probably not Fr/Hol

```
Have rejected 4 herds with butter fats over 5%. Previously, when selecting herds for this database dropped herds known to be NOT Hol/Fr from herd name, location (Channel Islands), personal knowledge. 

# look at distribution of the main driving KPI's - excl MY - is any trimming needed? 

```{r main KPIs EDA, echo=FALSE}

# pull out data point for a specific herd - here is is herd 1 which is HAU
xpoint = data$AAFC[farmNumber]
ypoint = 7
# create the percentile distribution
percentile = ecdf(data$AAFC)
# where does farm 1 lie on this distribution
m = 100* percentile(xpoint)
 # is.integer(m)
m = round(m+0.5,0)
m = as.integer(m)
 # is.integer(m)
m = as.character(m)
# using paste() to concatenate two strings
result = paste("Percent of herds in dataset that have a value lower than this farm = ", m)

p = ggplot(data, aes(x=AAFC))+
  geom_histogram(binwidth =14 ,fill = "cadetblue1", colour = "deepskyblue4" )+
      labs(y = "herds", 
        x = "Age at first calving (days)", 
        title = "AAFC - days",
        subtitle = "136 herds - as at 24July24",
        caption = result) +
           geom_point(aes(x=xpoint,y=ypoint), color="blue", size = 5)  +
     geom_label(
    label=farmName, 
    x=xpoint*1.13,
    y=ypoint*1.35,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.35,
    color = "bisque4",
    fill="bisque")

plot(p)

print ("Value for this herd :")
print(data$AAFC[farmNumber])

summary(data$AAFC)
# find the highest and lowest values 
# sort into a temp dataframe
tempData = data[order(data$AAFC),]
# look at top and bottom 
#head(tempData,10)
#tail(tempData,10)



# convert to months 
data$AAFCMonths = data$AAFC/30.4

# pull out data point for a specific herd - here is is herd 1 which is HAU
xpoint = data$AAFCMonths[farmNumber]
ypoint = 7
# create the percentile distribution
percentile = ecdf(data$AAFCMonths)
# where does farm 1 lie on this distribution
m = 100* percentile(xpoint)
 # is.integer(m)
m = round(m+0.5,0)
m = as.integer(m)
 # is.integer(m)
m = as.character(m)
# using paste() to concatenate two strings
result = paste("Percent of herds in dataset that have a value lower than this farm = ", m)

p = ggplot(data, aes(x=AAFCMonths))+
  geom_histogram(binwidth =.25 ,fill = "cadetblue1", colour = "deepskyblue4" )+
      labs(y = "herds", 
        x = "Age at first calving (months)", 
        title = "AAFC - months",
        subtitle = "136 herds - as at 24July24",
        caption = result) +
           geom_point(aes(x=xpoint,y=ypoint), color="blue", size = 5)  +
     geom_label(
    label=farmName, 
    x=xpoint*1.13,
    y=ypoint*1.35,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.35,
    color = "bisque4",
    fill="bisque")

plot(p)

print ("Value for this herd :")
print(data$AAFCMonths[farmNumber])

summary(data$AAFCMonths)
# find the highest and lowest values 
# sort into a temp dataframe
tempData = data[order(data$AAFCMonths),]
# look at top and bottom 
#head(tempData,10)
#tail(tempData,10)


# pull out data point for a specific herd - here is is herd 1 which is HAU
xpoint = data$CI[farmNumber]
ypoint = 7
# create the percentile distribution
percentile = ecdf(data$CI)
# where does farm 1 lie on this distribution
m = 100* percentile(xpoint)
 # is.integer(m)
m = round(m+0.5,0)
m = as.integer(m)
 # is.integer(m)
m = as.character(m)
# using paste() to concatenate two strings
result = paste("Percent of herds in dataset that have a value lower than this farm = ", m)


p = ggplot(data, aes(x=CI))+
  geom_histogram(binwidth =5 ,fill = "cadetblue1", colour = "deepskyblue4" )+
      labs(y = "herds", 
        x = "Calving Interval (days)", 
        title = "Calving Interval",
        subtitle = "136 herds - as at 24July24",
        caption = result) + 
          geom_point(aes(x=xpoint,y=ypoint), color="blue", size = 5)  +
     geom_label(
    label=farmName, 
    x=xpoint*1.13,
    y=ypoint*1.35,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.35,
    color = "bisque4",
    fill="bisque")
plot(p)

print ("Value for this herd :")
print(data$CI[farmNumber])

summary(data$CI)
tempData = data[order(data$CI),]
# look at top and bottom 
#head(tempData,10)
#tail(tempData,10)


# culling

# pull out data point for a specific herd - here is is herd 1 which is HAU
xpoint = data$culling[farmNumber]
ypoint = 7
# create the percentile distribution
percentile = ecdf(data$culling)
# where does farm 1 lie on this distribution
m = 100* percentile(xpoint)
 # is.integer(m)
m = round(m+0.5,0)
m = as.integer(m)
 # is.integer(m)
m = as.character(m)
# using paste() to concatenate two strings
result = paste("Percent of herds in dataset that have a value lower than this farm = ", m)

p = ggplot(data, aes(x=culling))+
  geom_histogram(binwidth =5 ,fill = "cadetblue1", colour = "deepskyblue4" )+
      labs(y = "herds", 
        x = "culling (% of herd)", 
        title = "Culling rate (% of herd/year)",
        subtitle = "136 herds - as at 24July24",
        caption = result) +
            geom_point(aes(x=xpoint,y=ypoint), color="blue", size = 5)  +
     geom_label(
    label=farmName, 
    x=xpoint*1.3,
    y=ypoint*1.5,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.35,
    color = "bisque4",
    fill="bisque")

plot(p)
print ("Value for this herd :")
print(data$culling[farmNumber])

summary(data$culling)
# find the highest and lowest values 
# sort into a temp dataframe
tempData = data[order(data$culling),]
# look at top and bottom 
#head(tempData,10)
#tail(tempData,10)

# ACTION - exclude all herds where culling rate is over 50% 

data = data[data$culling < 50 , ]

# Average lactation number when leave herd

# pull out data point for a specific herd - here is is herd 1 which is HAU
xpoint = data$avLactOnLeaving[farmNumber]
ypoint = 7
# create the percentile distribution
percentile = ecdf(data$avLactOnLeaving)
# where does farm 1 lie on this distribution
m = 100* percentile(xpoint)
 # is.integer(m)
m = round(m+0.5,0)
m = as.integer(m)
 # is.integer(m)
m = as.character(m)
# using paste() to concatenate two strings
result = paste("Percent of herds in dataset that have a value lower than this farm = ", m)

p = ggplot(data, aes(x=avLactOnLeaving))+
  geom_histogram(binwidth =0.25 ,fill = "cadetblue1", colour = "deepskyblue4" )+
      labs(y = "herds", 
        x = "Average lactation number when leave herd", 
        title = "Average lactation number when leave herd",
        subtitle = "136 herds - as at 24July24",
        caption = result) + 
            geom_point(aes(x=xpoint,y=ypoint), color="blue", size = 5)  +
     geom_label(
    label=farmName, 
    x=xpoint*1.13,
    y=ypoint*1.35,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.35,
    color = "bisque4",
    fill="bisque")
plot(p)

print ("Value for this herd :")
print(data$avLactOnLeaving[farmNumber])

summary(data$avLactOnLeaving)

tempData = data[order(data$avLactOnLeaving),]
# look at top and bottom 
#head(tempData,10)
#tail(tempData,10)

# finally just look at culling rate cf lactNo at culling 

plot(data$culling,data$avLactOnLeaving)
cor(data$culling,data$avLactOnLeaving)


```

Ten herds rejected as culling rates over 50%. Initially 149, 4 lost for high butterfat, 10 lost for high culling. 
14 removed out of 149 = 9.4% rejected. 


# finally look at distribution of eCO2 / kg FP Corr milk  



```{r Enteric methane EDA, echo=FALSE}
# pull out data point for a specific herd - here is is herd 1 which is HAU
xpoint = data$eCO2GWP100Total[farmNumber]
ypoint = 12

# create the percentile distribution
percentile = ecdf(data$eCO2GWP100Total)
# where does farm 1 lie on this distribution
m = 100* percentile(xpoint)
 # is.integer(m)
m = round(m+0.5,0)
m = as.integer(m)
 # is.integer(m)
m = as.character(m)
# using paste() to concatenate two strings
result = paste("Percent of herds in dataset that have a value lower than this farm = ", m)

p = ggplot(data, aes(x=eCO2GWP100Total))+
  geom_histogram(binwidth =0.025 ,fill = "cadetblue1", colour = "deepskyblue4" )+
      labs(y = "herds", 
        x = "kg eCO2 from enteric methane per kg milk (over lifetime) GWP100", 
        title = "kg eCO2 from enteric methane per kg milk (over lifetime)",
        subtitle = "135 herds - as at 24July24",
        # caption = "HPR LCA v05 24Jul24 data" )
        caption = result ) +
        geom_point(aes(x=xpoint,y=ypoint), color="blue", size = 5)  +
     geom_label(
    label=farmName, 
    x=xpoint*1.03,
    y=ypoint*1.2,
    label.padding = unit(0.55, "lines"), # Rectangle size around label
    label.size = 0.35,
    color = "bisque4",
    fill="bisque"
  )

plot(p)

print ("Value for this herd :")
print(data$eCO2GWP100Total[farmNumber])

summary(data$eCO2GWP100Total)

```
SUMMARY - have deleted 6 herds as they looked like Channel Island breed and 9 herds as culling rate was too high due to TB culls, selling down-calved heifers, or downsizing / closing up / retiring. 

Find out who are highest and lowest emitters

```{r min and max CH4 eCO2, echo=FALSE}

min(data$eCO2GWP100Total)
max(data$eCO2GWP100Total)

minCH4eCO2 = which.min(data$eCO2GWP100Total)
maxCH4eCO2 = which.max(data$eCO2GWP100Total)

data$farmID[minCH4eCO2]  # 108968101	C J & P H GEORGE, TRESILLIAN

data$farmID[maxCH4eCO2] # 97468901	D J  M J & P W HOUSE, STOKE ST GREGORY


```

Finally - in EDA - look at some simple regressions 

```{r simple regressions, echo=FALSE}

# milk yield 

p = ggplot(data, aes(x=annualMYFPCM, y=eCO2GWP100Total))+
  geom_point(size = 2) +
     labs(x = "Annual milk yield", 
        y = "kg eCO2 from enteric methane per kg milk (over lifetime) ?GWP100", 
        title = "kg eCO2 from enteric methane per kg milk (over lifetime) cf milk yield",
        subtitle = "136 herds - as at 24July24",
        caption = "HPR LCA v05 24Jul24 data" )
        # caption = result ) 

plot(p)

corr = cor(data$annualMYFPCM,data$eCO2GWP100Total)

print (corr)

# regression 

model = lm(eCO2GWP100Total ~ annualMYFPCM,data = data)

summary(model)

print (tidy(model))

par(mfrow = c(2, 2))
plot(model)
par(mfrow = c(1, 1))

#Assumptions made when fitting the regression look valid

# as it is such a strong effect (R2 = 0.75) should be be looking to model the residuals on the other factors 

# AAFC

p = ggplot(data, aes(x=AAFCMonths, y=eCO2GWP100Total))+
  geom_point(size = 2) +
     labs(x = "Age at first calving (months)", 
        y = "kg eCO2 from enteric methane per kg milk (over lifetime) ?GWP100", 
        title = "kg eCO2 from enteric methane per kg milk (over lifetime) cf milk yield",
        subtitle = "136 herds - as at 24July24",
        caption = "HPR LCA v05 24Jul24 data" )
 

plot(p)

corr = cor(data$AAFCMonths,data$eCO2GWP100Total)

print (corr)

# regression - AAFC

model = lm(eCO2GWP100Total~ AAFCMonths,data = data)

summary(model)

print (tidy(model))

# AAFC has a significant effect but variation accounted for is small at 15% 

par(mfrow = c(2, 2))
plot(model)
par(mfrow = c(1, 1))

# CI days

p = ggplot(data, aes(x=CI, y=eCO2GWP100Total))+
  geom_point(size = 2) +
     labs(x = "CI (days)", 
        y = "kg eCO2 from enteric methane per kg milk (over lifetime) ?GWP100", 
        title = "kg eCO2 from enteric methane per kg milk (over lifetime) cf milk yield",
        subtitle = "136 herds - as at 24July24",
        caption = "HPR LCA v05 24Jul24 data" )
 

plot(p)

corr = cor(data$CI,data$eCO2GWP100Total)

print (corr)

# regression 

model = lm(eCO2GWP100Total ~ CI,data = data)

summary(model)

print (tidy(model))

par(mfrow = c(2, 2))
plot(model)
par(mfrow = c(1, 1))

# the slope - effect of CI - is not signif different from zero

# culling 

p = ggplot(data, aes(x=culling, y=eCO2GWP100Total))+
  geom_point(size = 2) +
     labs(x = "Annual culling (%)", 
        y = "kg eCO2 from enteric methane per kg milk (over lifetime) ?GWP100", 
        title = "kg eCO2 from enteric methane per kg milk (over lifetime) cf milk yield",
        subtitle = "136 herds - as at 24July24",
        caption = "HPR LCA v05 24Jul24 data" )
 

plot(p)

corr = cor(data$culling,data$eCO2GWP100Total)

print (corr)

# regression 

model = lm(eCO2GWP100Total ~ culling,data = data)

summary(model)

print (tidy(model))

par(mfrow = c(2, 2))
plot(model)
par(mfrow = c(1, 1))

# not looking hopeful but need to remove the outlier(s) first 

# lact number at culling 

p = ggplot(data, aes(x=avLactOnLeaving, y=eCO2GWP100Total))+
  geom_point(size = 2) +
     labs(x = "Average lactation number when culled", 
        y = "kg eCO2 from enteric methane per kg milk (over lifetime) ?GWP100", 
        title = "kg eCO2 from enteric methane per kg milk (over lifetime) cf milk yield",
        subtitle = "136 herds - as at 24July24",
        caption = "HPR LCA v05 24Jul24 data" )
 

plot(p)

corr = cor(data$avLactOnLeaving,data$eCO2GWP100Total)

print (corr)

# multiple regression 

model = lm(eCO2GWP100Total ~ + avLactOnLeaving,data = data)

summary(model)

print (tidy(model))

par(mfrow = c(2, 2))
plot(model)
par(mfrow = c(1, 1))

# finally all together 

model = lm(eCO2GWP100Total ~ annualMYFPCM + AAFCMonths + CI + avLactOnLeaving + culling ,data = data)

summary(model)

print (tidy(model))

par(mfrow = c(2, 2))
plot(model)
par(mfrow = c(1, 1))

# now get a model that explains 87% of variance and all components are significant. 

# correlation matrix 
# select the variables wanted 

dataSelected = data[,c("farmID","eCO2GWP100Total","annualMY","annualMYFPCM","AAFCMonths","CI" , "avLactOnLeaving" , "culling")]



res = cor(dataSelected)
round(res, 2)

res2 = rcorr(as.matrix(dataSelected))
res2

p = chart.Correlation(dataSelected, histogram=TRUE, pch=19)

# finally save the data as a R dataset

save(data,file = "C:/ATC_data/HPRs/Paper_Eric_OEE+LCA/data_13Aug24_135herds")
save(dataSelected,file = "C:/ATC_data/HPRs/Paper_Eric_OEE+LCA/data_13Aug24_135_selected")

```
A very simple 5 component multiple regression model had a adj R2 of 89%, F=209 on df(5,129), p<0.001. Only culling was not significant in the model - I assume avLactOnLeaving took out most of this variables effect.  


This is not the same as sensitivity analysis which I would do with the model I have 

. Find an 'average herd' or typical herd - how? 
.. normalise each variable and express as SND's then look for the herd with the combined / average min absolute SND. 

. set all variables into model at the average values 
. vary one at a time to the decile values 

identify several 'typical' herds and so sens analysis on each herd and look at difference in results. 

This has been done in another R file. 

